Powdery mildew yield loss mitigation strategies in mungbean, a meta-analysis.

### 2020-01-28 DataWrangle/ExcludeBook_191115_PMMB_DataWrangling_PM.Rmd
Updated 2013 code

Herm_10_m <- Herm_10_dat %>%
   group_by(trial_ref, year, location, host_genotype, trial_design, trade_name,fungicide_ai,dose_ai.ha,n_treatment) %>%
   summarise(plot_length.m. = mean(plot_length, na.rm = TRUE),
              plot_width.m. = mean(plot_width, na.rm = TRUE),
              plant_density = unique(plant_density),
              row_spacing = unique(row_spacing),
              replicates = sum(replicate),
              planting_date = unique(planting_date),
              emergence_date = NA,
              flowering_date = NA,
              pod_fill_date = NA,
              mid_late_pod_fill = NA,
              first_sign_disease = unique(first_sign_disease),
              fungicide_application_1 = unique(fungicide_application_1),
              fungicide_application_2 = unique(fungicide_application_2),
              fungicide_application_3 = unique(fungicide_application_3),
              fungicide_application_4 = unique(fungicide_application_4),
              fungicide_application_5 = unique(fungicide_application_5),
             fungicide_application_6 = unique(fungicide_application_6),
             fungicide_application_6 = unique(fungicide_application_7),
              total_fungicide = unique(total_fungicide),
              harvest_date = unique(harvest_date),
              final_assessment = unique(final_assessment),
              PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
              rating_scale = unique(rating_scale),
              disease_error = sd(PM_final_severity, na.rm = TRUE),
              D_error_type = "stdev",
              grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
              raw_graded = NA,
              yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
              Y_error_type = "stdev",
              AUDPC.m = mean(AUDPC),
             AUDPC.sd = sd(AUDPC),
              meanSq = anova(lm(grain_yield.t.ha. ~ host_genotype + factor(n_treatment), data = Herm_10_dat))[2,3]
   )

@@

Herm_11_m <- Herm_11_dat %>%
   group_by(trial_ref, year, location, host_genotype, trial_design, trade_name,fungicide_ai,dose_ai.ha,n_treatment) %>%
   summarise(plot_length.m. = mean(plot_length, na.rm = TRUE),
              plot_width.m. = mean(plot_width, na.rm = TRUE),
              plant_density = unique(plant_density),
              row_spacing = unique(row_spacing),
              replicates = sum(replicate),
              planting_date = unique(planting_date),
              emergence_date = NA,
              flowering_date = unique(flowering_date),
              pod_fill_date = NA,
              mid_late_pod_fill = NA,
              first_sign_disease = unique(first_sign_disease),
              fungicide_application_1 = unique(fungicide_application_1),
              fungicide_application_2 = unique(fungicide_application_2),
              fungicide_application_3 = unique(fungicide_application_3),
              total_fungicide = unique(total_fungicide),
              harvest_date = unique(harvest_date),
              final_assessment = unique(final_assessment),
              PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
              rating_scale = unique(rating_scale),
              disease_error = sd(PM_final_severity, na.rm = TRUE),
              D_error_type = "stdev",
              grain_yield.t.ha. = mean(grain_yield.t.ha./1000, na.rm = TRUE),
              raw_graded = NA,
              yield_error = sd(grain_yield.t.ha./1000, na.rm = TRUE),
              Y_error_type = "stdev",
             AUDPC.m = mean(AUDPC),
             AUDPC.sd = sd(AUDPC),
              meanSq = anova(lm(grain_yield.t.ha./1000 ~ factor(n_treatment) + host_genotype, 
                                data = Herm_11_dat[Herm_11_dat$fungicide_ai == "tebuconazole" | 
                                                        Herm_11_dat$fungicide_ai == "control" ,]))[1,3]
   )

@@

King_11_m <- King_11_dat %>%
   group_by(trial_ref, year, location, host_genotype, trial_design, trade_name,fungicide_ai,dose_ai.ha,n_treatment) %>%
   summarise(plot_length.m. = mean(plot_length, na.rm = TRUE),
              plot_width.m. = mean(plot_width, na.rm = TRUE),
              plant_density = unique(plant_density),
              row_spacing = unique(row_spacing),
              replicates = sum(replicate),
              planting_date = unique(planting_date),
              emergence_date = NA,
              flowering_date = unique(flowering_date),
              pod_fill_date = NA,
              mid_late_pod_fill = NA,
              first_sign_disease = unique(first_sign_disease),
              fungicide_application_1 = unique(fungicide_application_1),
              fungicide_application_2 = unique(fungicide_application_2),
              fungicide_application_3 = unique(fungicide_application_3),
              total_fungicide = unique(total_fungicide),
              harvest_date = unique(harvest_date),
              final_assessment = unique(final_assessment),
              PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
              rating_scale = unique(rating_scale),
              disease_error = sd(PM_final_severity, na.rm = TRUE),
              D_error_type = "stdev",
              grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE)/1000,
              raw_graded = NA,
              yield_error = sd(grain_yield.t.ha./1000, na.rm = TRUE),
              Y_error_type = "stdev",
             AUDPC.m = mean(AUDPC),
             AUDPC.sd = sd(AUDPC),
              meanSq = anova(lm(grain_yield.t.ha./1000 ~ factor(n_treatment) + host_genotype, 
                                data = King_11_dat[King_11_dat$fungicide_ai == "tebuconazole" | 
                                                        King_11_dat$fungicide_ai == "control" ,]))[1,3]
   )

@@

Goolhi_13_m <- Goolhi_13_dat %>%
   group_by(trial_ref, year, location, host_genotype, trial_design, 
            trade_name,fungicide_ai,dose_ai.ha,n_treatment) %>%
   summarise(plot_length.m. = mean(plot_length, na.rm = TRUE),
              plot_width.m. = mean(plot_width, na.rm = TRUE),
              plant_density = unique(plant_density),
              row_spacing = unique(row_spacing),
              replicates = sum(replicate),
              planting_date = unique(planting_date),
              emergence_date = NA,
              flowering_date = unique(flowering_date),
              pod_fill_date = unique(pod_fill_date),
              mid_late_pod_fill = unique(mid_late_pod_fill),
              first_sign_disease = unique(first_sign_disease),
              fungicide_application_1 = unique(fungicide_application_1),
              fungicide_application_2 = unique(fungicide_application_2),
              fungicide_application_3 = unique(fungicide_application_3),
              total_fungicide = unique(total_fungicide),
              harvest_date = unique(harvest_date),
              final_assessment = unique(final_assessment),
              PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
              rating_scale = unique(rating_scale),
              disease_error = sd(PM_final_severity, na.rm = TRUE),
              D_error_type = "stdev",
              grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
              raw_graded = NA,
              yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
              Y_error_type = "stdev",
             AUDPC.m = mean(AUDPC),
             AUDPC.sd = sd(AUDPC),
              meanSq = anova(lm(grain_yield.t.ha. ~ factor(total_fungicide), 
                                data = Goolhi_13_dat[Goolhi_13_dat$fungicide_ai == "propiconazole" | 
                                                        Goolhi_13_dat$fungicide_ai == "control" ,]))[1,3]
   )

@@

#### Calculating the treatment means
```{r Marys_means}
MarysM_13_m <- MarysM_13_dat %>%
   group_by(trial_ref, year, location, host_genotype, trial_design, 
            trade_name,fungicide_ai,dose_ai.ha,n_treatment) %>%
   summarise(plot_length.m. = mean(plot_length, na.rm = TRUE),
              plot_width.m. = mean(plot_width, na.rm = TRUE),
              plant_density = unique(plant_density),
              row_spacing = unique(row_spacing),
              replicates = length(as.numeric(replicate)),
              planting_date = unique(planting_date),
              emergence_date = NA,
              flowering_date = unique(flowering_date),
              pod_fill_date = unique(pod_fill_date),
              mid_late_pod_fill = unique(mid_late_pod_fill),
              first_sign_disease = unique(first_sign_disease),
              fungicide_application_1 = unique(fungicide_application_1),
              fungicide_application_2 = unique(fungicide_application_2),
              fungicide_application_3 = unique(fungicide_application_3),
              total_fungicide = unique(total_fungicide),
              harvest_date = unique(harvest_date),
              final_assessment = unique(final_assessment),
              PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
              rating_scale = unique(rating_scale),
              disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
              D_error_type = "stdev",
              grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
              raw_graded = NA,
              yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
              Y_error_type = "stdev",
             AUDPC.m = mean(AUDPC),
             AUDPC.sd = sd(AUDPC),
              meanSq = anova(lm(grain_yield.t.ha. ~ factor(total_fungicide), 
                                data = MarysM_13_dat[MarysM_13_dat$fungicide_ai == "propiconazole" | 
                                                        MarysM_13_dat$fungicide_ai == "control" ,]))[1,3]

@@

   if (i == length(Premer.13D[, 1])) {
      print(!plotsRecorded)
   }
}
# remove Plots not surveyed
Premer.13D <- Premer.13D[!plotsRecorded, ]

@@

#### Calculating the treatment means
```{r Prem13_TreatmentMeans}
Premer_13_m <- Premer_13_dat %>%
   group_by(trial_ref, year, location, host_genotype, trial_design, 
            trade_name,fungicide_ai,dose_ai.ha,n_treatment) %>%
   summarise(plot_length.m. = mean(plot_length, na.rm = TRUE),
              plot_width.m. = mean(plot_width, na.rm = TRUE),
              plant_density = unique(plant_density),
              row_spacing = unique(row_spacing),
              replicates = sum(as.numeric(replicate)),
              planting_date = unique(planting_date),
              emergence_date = NA,
              flowering_date = unique(flowering_date),
              pod_fill_date = unique(pod_fill_date),
              mid_late_pod_fill = unique(mid_late_pod_fill),
              first_sign_disease = unique(first_sign_disease),
              fungicide_application_1 = unique(fungicide_application_1),
              fungicide_application_2 = unique(fungicide_application_2),
              fungicide_application_3 = unique(fungicide_application_3),
              total_fungicide = unique(total_fungicide),
              harvest_date = unique(harvest_date),
              final_assessment = unique(final_assessment),
              PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
              rating_scale = unique(rating_scale),
              disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
              D_error_type = "stdev",
              grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
              raw_graded = NA,
              yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
              Y_error_type = "stdev",
             AUDPC.m = mean(AUDPC),
             AUDPC.sd = sd(AUDPC),
              meanSq = anova(lm(grain_yield.t.ha. ~ factor(total_fungicide), 
                                data = Premer_13_dat[Premer_13_dat$fungicide_ai == "propiconazole" | 
                                                        Premer_13_dat$fungicide_ai == "control" ,]))[1,3]
   )

@@

write.csv(
   Premer_13_m[order(as.numeric(Premer_13_m$n_treatment)),],
   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2013/BB1305_Millmerran_means.csv",
   row.names = FALSE
)
##########################
# For some wierd reason standard deviations are comming back NA in the code above
Premer_13_m[,c("disease_error","yield_error")] <- 
   Premer_13_dat %>%
   group_by(n_treatment) %>%
   summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
             yield_error = sd(grain_yield.t.ha., na.rm = TRUE)) %>%
   select(c("disease_error","yield_error"))

@@

Premer_13_m <- Premer_13_m[Premer_13_m$trade_name != "other",]

@@

# read in yield and format
# read in yield and format
Millm.13Y <-
   as.data.frame(
      read_xlsx(
         path = "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2013/BB1305 Fungicides for powdery mildew in mungbean - Millmerran.xlsx",
         sheet = "Harvest Sheet 6.5.2013",
         range = "A11:F55",
         col_names = TRUE
      )
   )
Millm.13Y$Treatment <- as.character(Millm.13Y$Treatment)
Millm.13Y$Treat <- as.double(Millm.13Y$Treat)
colnames(Millm.13Y)[1:4] <- c("Run", "Plot","TreatY", "Rep")

@@

Millm_13_dat <- 
   data.frame(trial_ref = "BB1305",
              year = "2013",
              location = "Millmerran",
              host_genotype = "Crystal",
              trial_design = "RCB",
              plot_length = 12,
              plot_width = 4,
              plant_density = as.Date(NA),
              row_spacing = 1/3,
              replicate = Millm_13$Rep,
              planting_date = as.Date(NA),
              emergence_date = as.Date(NA),
              flowering_date = as.Date(NA),
              pod_fill_date = as.Date("2013-03-21", format = "%Y-%m-%d"),
              mid_late_pod_fill = as.Date("2013-03-28", format = "%Y-%m-%d"),
              first_sign_disease = as.Date("2013-03-13", format = "%Y-%m-%d"),
              trade_name = as.factor(Millm_13$trade_name),
              fungicide_ai = Millm_13$fungicide_ai,
              dose_ai.ha = Millm_13$dose_ai.ha,
              n_treatment = Millm_13$Treat,
              fungicide_application_1 = Millm_13$fungicide_application_1,
              fungicide_application_2 = Millm_13$fungicide_application_2,
              fungicide_application_3 = Millm_13$fungicide_application_3,
              total_fungicide = Millm_13$spray_n,
              harvest_date = as.Date("2013-05-06", format = "%Y-%m-%d"),
              final_assessment = as.Date("2013-04-24", format = "%Y-%m-%d"),
              PM_final_severity = Millm_13$Inc_42D,
              rating_scale = "1-9",
              grain_yield.t.ha. = as.numeric(Millm_13$`kg/Ha`)/1000
              #AUDPC = apply(Millm_13[,c("Inc_23D","Inc_42D")]-1,1, FUN = audpc, dates = c(23,42)) # -1 to the data because zero disease = 1 on rating scale// Dates are based off days from first sign
              )

Millm_13_dat <- cbind(Millm_13_dat,
                          AUDPC = apply(data.frame(zero = 1,
                                                   Millm_13[,c("Inc_23D","Inc_42D")]-1),
                                        1, 
                                        FUN = audpc, 
                                        dates = c((Millm_13_dat$first_sign_disease[1]-7)-
                                                     Millm_13_dat$planting_date[1],
                                                  23,42)
                                        )
                          )
```

#### Calculating the treatment means
```{r Millm13_TreatmentMeans}
Millm_13_m <- Millm_13_dat %>%
   group_by(trial_ref, year, location, host_genotype, trial_design, 
            trade_name,fungicide_ai,dose_ai.ha,n_treatment) %>%
   summarise(plot_length.m. = mean(plot_length, na.rm = TRUE),
             plot_width.m. = mean(plot_width, na.rm = TRUE),
             plant_density = unique(plant_density),
             row_spacing = unique(row_spacing),
             replicates = length(as.numeric(replicate)),
             planting_date = unique(planting_date),
             emergence_date = NA,
             flowering_date = unique(flowering_date),
             pod_fill_date = unique(pod_fill_date),
             mid_late_pod_fill = unique(mid_late_pod_fill),
             first_sign_disease = unique(first_sign_disease),
             fungicide_application_1 = unique(fungicide_application_1),
             fungicide_application_2 = unique(fungicide_application_2),
             fungicide_application_3 = unique(fungicide_application_3),
             total_fungicide = unique(total_fungicide),
             harvest_date = unique(harvest_date),
             final_assessment = unique(final_assessment),
             PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
             rating_scale = unique(rating_scale),
             disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
             D_error_type = "stdev",
             grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
             raw_graded = NA,
             yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
             Y_error_type = "stdev",
             AUDPC.m = mean(AUDPC),
             AUDPC.sd = sd(AUDPC),
             meanSq = anova(lm(grain_yield.t.ha. ~ factor(total_fungicide), 
                                data = Millm_13_dat[Millm_13_dat$fungicide_ai == "propiconazole" | 
                                                        Millm_13_dat$fungicide_ai == "control" ,]))[1,3]
   )

@@

Herm_16_m <- fold_data(Herm_16_m, PM_MB_means)
Herm_16_m <- Herm_16_m[,!colnames(Herm_16_m) %in% c('Treatment',"dae24","dae38","dae48","dae63","Final_Yield_tHa", "AUDPC.m")]

@@

King_16_m <- fold_data(King_16_m, PM_MB_means)
King_16_m <- King_16_m[,!colnames(King_16_m) %in% c('Treatment',"dae20","dae34","dae46","Final_Yield_tHa", "AUDPC.m")]

>>>>

Herm_10_m <- Herm_10_dat %>%
   group_by(trial_ref, year, location, host_genotype, trial_design, trade_name,fungicide_ai,dose_ai.ha,n_treatment) %>%
   summarise(plot_length.m. = mean(plot_length, na.rm = TRUE),
              plot_width.m. = mean(plot_width, na.rm = TRUE),
              plant_density = unique(plant_density),
              row_spacing = unique(row_spacing),
              replicates = sum(replicate),
              planting_date = unique(planting_date),
              emergence_date = NA,
              flowering_date = NA,
              pod_fill_date = NA,
              mid_late_pod_fill = NA,
              first_sign_disease = unique(first_sign_disease),
              fungicide_application_1 = unique(fungicide_application_1),
              fungicide_application_2 = unique(fungicide_application_2),
              fungicide_application_3 = unique(fungicide_application_3),
              fungicide_application_4 = unique(fungicide_application_4),
              fungicide_application_5 = unique(fungicide_application_5),
             fungicide_application_6 = unique(fungicide_application_6),
             fungicide_application_6 = unique(fungicide_application_7),
              total_fungicide = unique(total_fungicide),
              harvest_date = unique(harvest_date),
              final_assessment = unique(final_assessment),
              PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
              rating_scale = unique(rating_scale),
              disease_error = sd(PM_final_severity, na.rm = TRUE),
              D_error_type = "stdev",
              grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
              raw_graded = NA,
              yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
              Y_error_type = "stdev",
              AUDPC_m = mean(AUDPC),
             AUDPC_sd = sd(AUDPC),
              Y_Msquare = anova(lm(grain_yield.t.ha. ~ host_genotype + factor(n_treatment), data = Herm_10_dat))[2,3]
   )

@@

Herm_11_m <- Herm_11_dat %>%
   group_by(trial_ref, year, location, host_genotype, trial_design, trade_name,fungicide_ai,dose_ai.ha,n_treatment) %>%
   summarise(plot_length.m. = mean(plot_length, na.rm = TRUE),
              plot_width.m. = mean(plot_width, na.rm = TRUE),
              plant_density = unique(plant_density),
              row_spacing = unique(row_spacing),
              replicates = sum(replicate),
              planting_date = unique(planting_date),
              emergence_date = NA,
              flowering_date = unique(flowering_date),
              pod_fill_date = NA,
              mid_late_pod_fill = NA,
              first_sign_disease = unique(first_sign_disease),
              fungicide_application_1 = unique(fungicide_application_1),
              fungicide_application_2 = unique(fungicide_application_2),
              fungicide_application_3 = unique(fungicide_application_3),
              total_fungicide = unique(total_fungicide),
              harvest_date = unique(harvest_date),
              final_assessment = unique(final_assessment),
              PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
              rating_scale = unique(rating_scale),
              disease_error = sd(PM_final_severity, na.rm = TRUE),
              D_error_type = "stdev",
              grain_yield.t.ha. = mean(grain_yield.t.ha./1000, na.rm = TRUE),
              raw_graded = NA,
              yield_error = sd(grain_yield.t.ha./1000, na.rm = TRUE),
              Y_error_type = "stdev",
             AUDPC_m = mean(AUDPC),
             AUDPC_sd = sd(AUDPC),
              Y_Msquare = anova(lm(grain_yield.t.ha./1000 ~ factor(n_treatment) + host_genotype, 
                                data = Herm_11_dat[Herm_11_dat$fungicide_ai == "tebuconazole" | 
                                                        Herm_11_dat$fungicide_ai == "control" ,]))[1,3]
   )

@@

King_11_m <- King_11_dat %>%
   group_by(trial_ref, year, location, host_genotype, trial_design, trade_name,fungicide_ai,dose_ai.ha,n_treatment) %>%
   summarise(plot_length.m. = mean(plot_length, na.rm = TRUE),
              plot_width.m. = mean(plot_width, na.rm = TRUE),
              plant_density = unique(plant_density),
              row_spacing = unique(row_spacing),
              replicates = sum(replicate),
              planting_date = unique(planting_date),
              emergence_date = NA,
              flowering_date = unique(flowering_date),
              pod_fill_date = NA,
              mid_late_pod_fill = NA,
              first_sign_disease = unique(first_sign_disease),
              fungicide_application_1 = unique(fungicide_application_1),
              fungicide_application_2 = unique(fungicide_application_2),
              fungicide_application_3 = unique(fungicide_application_3),
              total_fungicide = unique(total_fungicide),
              harvest_date = unique(harvest_date),
              final_assessment = unique(final_assessment),
              PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
              rating_scale = unique(rating_scale),
              disease_error = sd(PM_final_severity, na.rm = TRUE),
              D_error_type = "stdev",
              grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE)/1000,
              raw_graded = NA,
              yield_error = sd(grain_yield.t.ha./1000, na.rm = TRUE),
              Y_error_type = "stdev",
             AUDPC_m = mean(AUDPC),
             AUDPC_sd = sd(AUDPC),
              Y_Msquare = anova(lm(grain_yield.t.ha./1000 ~ factor(n_treatment) + host_genotype, 
                                data = King_11_dat[King_11_dat$fungicide_ai == "tebuconazole" | 
                                                        King_11_dat$fungicide_ai == "control" ,]))[1,3]
   )

@@

Goolhi_13_m <- Goolhi_13_dat %>%
   group_by(trial_ref, year, location, host_genotype, trial_design, 
            trade_name,fungicide_ai,dose_ai.ha,n_treatment) %>%
   summarise(plot_length.m. = mean(plot_length, na.rm = TRUE),
              plot_width.m. = mean(plot_width, na.rm = TRUE),
              plant_density = unique(plant_density),
              row_spacing = unique(row_spacing),
              replicates = sum(replicate),
              planting_date = unique(planting_date),
              emergence_date = NA,
              flowering_date = unique(flowering_date),
              pod_fill_date = unique(pod_fill_date),
              mid_late_pod_fill = unique(mid_late_pod_fill),
              first_sign_disease = unique(first_sign_disease),
              fungicide_application_1 = unique(fungicide_application_1),
              fungicide_application_2 = unique(fungicide_application_2),
              fungicide_application_3 = unique(fungicide_application_3),
              total_fungicide = unique(total_fungicide),
              harvest_date = unique(harvest_date),
              final_assessment = unique(final_assessment),
              PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
              rating_scale = unique(rating_scale),
              disease_error = sd(PM_final_severity, na.rm = TRUE),
              D_error_type = "stdev",
              grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
              raw_graded = NA,
              yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
              Y_error_type = "stdev",
             AUDPC_m = mean(AUDPC),
             AUDPC_sd = sd(AUDPC),
              Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(total_fungicide), 
                                data = Goolhi_13_dat[Goolhi_13_dat$fungicide_ai == "propiconazole" | 
                                                        Goolhi_13_dat$fungicide_ai == "control" ,]))[1,3]
   )

@@

#### Calculating the treatment means
```{r Marys_means}
MarysM_13_m <- MarysM_13_dat %>%
   group_by(trial_ref, year, location, host_genotype, trial_design, 
            trade_name,fungicide_ai,dose_ai.ha,n_treatment) %>%
   summarise(plot_length.m. = mean(plot_length, na.rm = TRUE),
              plot_width.m. = mean(plot_width, na.rm = TRUE),
              plant_density = unique(plant_density),
              row_spacing = unique(row_spacing),
              replicates = length(as.numeric(replicate)),
              planting_date = unique(planting_date),
              emergence_date = NA,
              flowering_date = unique(flowering_date),
              pod_fill_date = unique(pod_fill_date),
              mid_late_pod_fill = unique(mid_late_pod_fill),
              first_sign_disease = unique(first_sign_disease),
              fungicide_application_1 = unique(fungicide_application_1),
              fungicide_application_2 = unique(fungicide_application_2),
              fungicide_application_3 = unique(fungicide_application_3),
              total_fungicide = unique(total_fungicide),
              harvest_date = unique(harvest_date),
              final_assessment = unique(final_assessment),
              PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
              rating_scale = unique(rating_scale),
              disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
              D_error_type = "stdev",
              grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
              raw_graded = NA,
              yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
              Y_error_type = "stdev",
             AUDPC_m = mean(AUDPC),
             AUDPC_sd = sd(AUDPC),
              Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(total_fungicide), 
                                data = MarysM_13_dat[MarysM_13_dat$fungicide_ai == "propiconazole" | 
                                                        MarysM_13_dat$fungicide_ai == "control" ,]))[1,3]

@@

   if (i == length(Premer.13D[, 1])) {
      #print(!plotsRecorded)
   }
}
# remove Plots not surveyed
Premer.13D <- Premer.13D[!plotsRecorded, ]

@@

#### Calculating the treatment means
```{r Prem13_TreatmentMeans}
Premer_13_m <- Premer_13_dat %>%
   group_by(n_treatment) %>%
   summarise(trial_ref = unique(trial_ref),
             year = unique(year),
             location = unique(location),
             host_genotype = unique(host_genotype),
             trial_design = unique(trial_design),
             trade_name = unique(trade_name),
             fungicide_ai = unique(fungicide_ai),
             dose_ai.ha = unique(dose_ai.ha),
            plot_length.m. = mean(plot_length, na.rm = TRUE),
              plot_width.m. = mean(plot_width, na.rm = TRUE),
              plant_density = unique(plant_density),
              row_spacing = unique(row_spacing),
              replicates = length(as.numeric(replicate)),
              planting_date = unique(planting_date),
              emergence_date = NA,
              flowering_date = unique(flowering_date),
              pod_fill_date = unique(pod_fill_date),
              mid_late_pod_fill = unique(mid_late_pod_fill),
              first_sign_disease = unique(first_sign_disease),
              fungicide_application_1 = unique(fungicide_application_1),
              fungicide_application_2 = unique(fungicide_application_2),
              fungicide_application_3 = unique(fungicide_application_3),
              total_fungicide = unique(total_fungicide),
              harvest_date = unique(harvest_date),
              final_assessment = unique(final_assessment),
              PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
              rating_scale = unique(rating_scale),
              disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
              D_error_type = "stdev",
              grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
              raw_graded = NA,
              yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
              Y_error_type = "stdev",
             AUDPC_m = mean(AUDPC),
             AUDPC_sd = sd(AUDPC),
              Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(total_fungicide), 
                                data = Premer_13_dat[Premer_13_dat$fungicide_ai == "propiconazole" | 
                                                        Premer_13_dat$fungicide_ai == "control" ,]))[1,3]
   )

@@

##########################
# For some wierd reason standard deviations are comming back NA in the code above
Premer_13_m[,c("disease_error","yield_error")] <- 
   Premer_13_dat %>%
   group_by(n_treatment) %>%
   summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
             yield_error = sd(grain_yield.t.ha., na.rm = TRUE)) %>%
   select(c("disease_error","yield_error"))

@@

#Premer_13_m <- Premer_13_m[Premer_13_m$trade_name != "other",]

@@

# read in yield and format
Millm.13Y <-
   as.data.frame(
      read_xlsx(
         path = "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2013/BB1305 Fungicides for powdery mildew in mungbean - Millmerran.xlsx",
         sheet = "Harvest Sheet 6.5.2013",
         range = "A11:F55",
         col_names = TRUE
      )
   )
Millm.13Y$Treatment <- as.character(Millm.13Y$Treatment)
Millm.13Y$Treat <- as.double(Millm.13Y$Treat)
colnames(Millm.13Y)[1:4] <- c("Run", "Plot","TreatY", "Rep")

@@

Millm_13_dat <- 
   data.frame(trial_ref = "BB1305",
              year = "2013",
              location = "Millmerran",
              host_genotype = "Crystal",
              trial_design = "RCB",
              plot_length = 12,
              plot_width = 4,
              plant_density = as.Date(NA),
              row_spacing = 1/3,
              replicate = Millm_13$Rep,
              planting_date = as.Date(NA),
              emergence_date = as.Date(NA),
              flowering_date = as.Date(NA),
              pod_fill_date = as.Date("2013-03-21", format = "%Y-%m-%d"),
              mid_late_pod_fill = as.Date("2013-03-28", format = "%Y-%m-%d"),
              first_sign_disease = as.Date("2013-03-13", format = "%Y-%m-%d"),
              trade_name = as.factor(Millm_13$trade_name),
              fungicide_ai = Millm_13$fungicide_ai,
              dose_ai.ha = Millm_13$dose_ai.ha,
              n_treatment = Millm_13$Treat,
              fungicide_application_1 = Millm_13$fungicide_application_1,
              fungicide_application_2 = Millm_13$fungicide_application_2,
              fungicide_application_3 = Millm_13$fungicide_application_3,
              total_fungicide = Millm_13$spray_n,
              harvest_date = as.Date("2013-05-06", format = "%Y-%m-%d"),
              final_assessment = as.Date("2013-04-24", format = "%Y-%m-%d"),
              PM_final_severity = Millm_13$Inc_42D,
              rating_scale = "1-9",
              grain_yield.t.ha. = as.numeric(Millm_13$`kg/Ha`)/1000,
              #AUDPC = apply(Millm_13[,c("Inc_23D","Inc_42D")]-1,1, FUN = audpc, dates = c(23,42)) # -1 to the data because zero disease = 1 on rating scale// Dates are based off days from first sign
              stringsAsFactors = FALSE)

Millm_13_dat <- cbind(Millm_13_dat,
                          AUDPC = apply(data.frame(zero = 1,
                                                   Millm_13[,c("Inc_23D","Inc_42D")]-1),
                                        1, 
                                        FUN = audpc, 
                                        dates = c(1,23,42)
                                        )
                          )
```

#### Calculating the treatment means
```{r Millm13_TreatmentMeans}
Millm_13_m <- Millm_13_dat %>%
   group_by(trial_ref, year, location, host_genotype, trial_design, 
            trade_name,fungicide_ai,dose_ai.ha,n_treatment) %>%
   summarise(plot_length.m. = mean(plot_length, na.rm = TRUE),
             plot_width.m. = mean(plot_width, na.rm = TRUE),
             plant_density = unique(plant_density),
             row_spacing = unique(row_spacing),
             replicates = length(as.numeric(replicate)),
             planting_date = unique(planting_date),
             emergence_date = NA,
             flowering_date = unique(flowering_date),
             pod_fill_date = unique(pod_fill_date),
             mid_late_pod_fill = unique(mid_late_pod_fill),
             first_sign_disease = unique(first_sign_disease),
             fungicide_application_1 = unique(fungicide_application_1),
             fungicide_application_2 = unique(fungicide_application_2),
             fungicide_application_3 = unique(fungicide_application_3),
             total_fungicide = unique(total_fungicide),
             harvest_date = unique(harvest_date),
             final_assessment = unique(final_assessment),
             PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
             rating_scale = unique(rating_scale),
             disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
             D_error_type = "stdev",
             grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
             raw_graded = NA,
             yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
             Y_error_type = "stdev",
             AUDPC_m = mean(AUDPC),
             AUDPC_sd = sd(AUDPC),
             Y_Msquare = anova(lm(grain_yield.t.ha. ~ factor(total_fungicide), 
                                data = Millm_13_dat[Millm_13_dat$fungicide_ai == "propiconazole" | 
                                                        Millm_13_dat$fungicide_ai == "control" ,]))[1,3]
   )

@@

Herm_16_m <- fold_data(Herm_16_m, PM_MB_means)
Herm_16_m <- Herm_16_m[,!colnames(Herm_16_m) %in% c('Treatment',"dae24","dae38","dae48","dae63","Final_Yield_tHa", "AUDPC_m")]

@@

King_16_m <- fold_data(King_16_m, PM_MB_means)
King_16_m <- King_16_m[,!colnames(King_16_m) %in% c('Treatment',"dae20","dae34","dae46","Final_Yield_tHa", "AUDPC_m")]
